MRD_final_microbiome

### 2019-06-28 import_popln_data.Rmd
updated

# Run function and change name
mnd.incidence <- mb.gather(mnd.incidence)
colnames(mnd.incidence)[2] <- "incidence 2017"

mnd.i.12 <- mb.gather(mnd.i.12)
colnames(mnd.i.12)[2] <- "incidence 2012"
mnd.i.13 <- mb.gather(mnd.i.13)
colnames(mnd.i.13)[2] <- "incidence 2013"
mnd.i.14 <- mb.gather(mnd.i.14)
colnames(mnd.i.14)[2] <- "incidence 2014"
mnd.i.15 <- mb.gather(mnd.i.15)
colnames(mnd.i.15)[2] <- "incidence 2015"
mnd.i.16 <- mb.gather(mnd.i.16)
colnames(mnd.i.16)[2] <- "incidence 2016"
mnd.roc.i <- mb.gather(mnd.roc.i)
colnames(mnd.roc.i)[2] <- "ROC incidence"

mnd.prev <- mb.gather(mnd.prev)
colnames(mnd.prev)[2] <- "prevalance 2017"
mnd.p.12 <- mb.gather(mnd.p.12)
colnames(mnd.p.12)[2] <- "prevalance 2012"
mnd.p.13 <- mb.gather(mnd.p.13)
colnames(mnd.p.13)[2] <- "prevalance 2013"
mnd.p.14 <- mb.gather(mnd.p.14)
colnames(mnd.p.14)[2] <- "prevalance 2014"
mnd.p.15 <- mb.gather(mnd.p.15)
colnames(mnd.p.15)[2] <- "prevalance 2015"
mnd.p.16 <- mb.gather(mnd.p.16)
colnames(mnd.p.16)[2] <- "prevalance 2016"
mnd.roc.p <- mb.gather(mnd.roc.p)
colnames(mnd.roc.p)[2] <- "ROC prevalance"

@@

mnd.i <- list( mnd.i.12, mnd.i.13,mnd.i.14,mnd.i.15,mnd.i.16,mnd.incidence,mnd.roc.i) %>% reduce(left_join, by = "Location")

mnd.p <- list( mnd.p.12, mnd.p.13,mnd.p.14,mnd.p.15,mnd.p.16,mnd.incidence,mnd.roc.p) %>% reduce(left_join, by = "Location")

@@

# Run function and change name
ipd.incidence <- mb.gather(ipd.incidence)
colnames(ipd.incidence)[2] <- "incidence 2017"

ipd.i.12 <- mb.gather(ipd.i.12)
colnames(ipd.i.12)[2] <- "incidence 2012"
ipd.i.13 <- mb.gather(ipd.i.13)
colnames(ipd.i.13)[2] <- "incidence 2013"
ipd.i.14 <- mb.gather(ipd.i.14)
colnames(ipd.i.14)[2] <- "incidence 2014"
ipd.i.15 <- mb.gather(ipd.i.15)
colnames(ipd.i.15)[2] <- "incidence 2015"
ipd.i.16 <- mb.gather(ipd.i.16)
colnames(ipd.i.16)[2] <- "incidence 2016"
ipd.roc.i <- mb.gather(ipd.roc.i)
colnames(ipd.roc.i)[2] <- "ROC incidence"

ipd.prev <- mb.gather(ipd.prev)
colnames(ipd.prev)[2] <- "prevalance 2017"
ipd.p.12 <- mb.gather(ipd.p.12)
colnames(ipd.p.12)[2] <- "prevalance 2012"
ipd.p.13 <- mb.gather(ipd.p.13)
colnames(ipd.p.13)[2] <- "prevalance 2013"
ipd.p.14 <- mb.gather(ipd.p.14)
colnames(ipd.p.14)[2] <- "prevalance 2014"
ipd.p.15 <- mb.gather(ipd.p.15)
colnames(ipd.p.15)[2] <- "prevalance 2015"
ipd.p.16 <- mb.gather(ipd.p.16)
colnames(ipd.p.16)[2] <- "prevalance 2016"
ipd.roc.p <- mb.gather(ipd.roc.p)
colnames(ipd.roc.p)[2] <- "ROC prevalance"

@@

ipd.i <- list( ipd.i.12, ipd.i.13,ipd.i.14,ipd.i.15,ipd.i.16,ipd.incidence,ipd.roc.i) %>% reduce(left_join, by = "Location")

ipd.p <- list( ipd.p.12, ipd.p.13,ipd.p.14,ipd.p.15,ipd.p.16,ipd.incidence,ipd.roc.p) %>% reduce(left_join, by = "Location")

@@

# Run function and change name
ad.incidence <- mb.gather(ad.incidence)
colnames(ad.incidence)[2] <- "incidence 2017"

ad.i.12 <- mb.gather(ad.i.12)
colnames(ad.i.12)[2] <- "incidence 2012"
ad.i.13 <- mb.gather(ad.i.13)
colnames(ad.i.13)[2] <- "incidence 2013"
ad.i.14 <- mb.gather(ad.i.14)
colnames(ad.i.14)[2] <- "incidence 2014"
ad.i.15 <- mb.gather(ad.i.15)
colnames(ad.i.15)[2] <- "incidence 2015"
ad.i.16 <- mb.gather(ad.i.16)
colnames(ad.i.16)[2] <- "incidence 2016"
ad.roc.i <- mb.gather(ad.roc.i)
colnames(ad.roc.i)[2] <- "ROC incidence"

ad.prev <- mb.gather(ad.prev)
colnames(ad.prev)[2] <- "prevalance 2017"
ad.p.12 <- mb.gather(ad.p.12)
colnames(ad.p.12)[2] <- "prevalance 2012"
ad.p.13 <- mb.gather(ad.p.13)
colnames(ad.p.13)[2] <- "prevalance 2013"
ad.p.14 <- mb.gather(ad.p.14)
colnames(ad.p.14)[2] <- "prevalance 2014"
ad.p.15 <- mb.gather(ad.p.15)
colnames(ad.p.15)[2] <- "prevalance 2015"
ad.p.16 <- mb.gather(ad.p.16)
colnames(ad.p.16)[2] <- "prevalance 2016"
ad.roc.p <- mb.gather(ad.roc.p)
colnames(ad.roc.p)[2] <- "ROC prevalance"

@@

ad.i <- list( ad.i.12, ad.i.13,ad.i.14,ad.i.15,ad.i.16,ad.incidence,ad.roc.i) %>% reduce(left_join, by = "Location")

ad.p <- list( ad.p.12, ad.p.13,ad.p.14,ad.p.15,ad.p.16,ad.incidence,ad.roc.p) %>% reduce(left_join, by = "Location")

>>>>

# Run function and change name
mnd.incidence <- mb.gather(mnd.incidence)
colnames(mnd.incidence)[2] <- 2017

mnd.i.12 <- mb.gather(mnd.i.12)
colnames(mnd.i.12)[2] <- 2012
mnd.i.13 <- mb.gather(mnd.i.13)
colnames(mnd.i.13)[2] <- 2013
mnd.i.14 <- mb.gather(mnd.i.14)
colnames(mnd.i.14)[2] <- 2014
mnd.i.15 <- mb.gather(mnd.i.15)
colnames(mnd.i.15)[2] <- 2015
mnd.i.16 <- mb.gather(mnd.i.16)
colnames(mnd.i.16)[2] <- 2016
#mnd.roc.i <- mb.gather(mnd.roc.i)
#colnames(mnd.roc.i)[2] <- "ROC incidence"

mnd.prev <- mb.gather(mnd.prev)
colnames(mnd.prev)[2] <- 2017
mnd.p.12 <- mb.gather(mnd.p.12)
colnames(mnd.p.12)[2] <- 2012
mnd.p.13 <- mb.gather(mnd.p.13)
colnames(mnd.p.13)[2] <- 2013
mnd.p.14 <- mb.gather(mnd.p.14)
colnames(mnd.p.14)[2] <- 2014
mnd.p.15 <- mb.gather(mnd.p.15)
colnames(mnd.p.15)[2] <- 2015
mnd.p.16 <- mb.gather(mnd.p.16)
colnames(mnd.p.16)[2] <- 2016
#mnd.roc.p <- mb.gather(mnd.roc.p)
#colnames(mnd.roc.p)[2] <- "ROC prevalance"

@@

mnd.i <- list( mnd.i.12, mnd.i.13,mnd.i.14,mnd.i.15,mnd.i.16,mnd.incidence) %>% reduce(left_join, by = "Location")

mnd.p <- list( mnd.p.12, mnd.p.13,mnd.p.14,mnd.p.15,mnd.p.16,mnd.incidence) %>% reduce(left_join, by = "Location")

@@

# Run function and change name
ipd.incidence <- mb.gather(ipd.incidence)
colnames(ipd.incidence)[2] <- 2017

ipd.i.12 <- mb.gather(ipd.i.12)
colnames(ipd.i.12)[2] <- 2012
ipd.i.13 <- mb.gather(ipd.i.13)
colnames(ipd.i.13)[2] <- 2013
ipd.i.14 <- mb.gather(ipd.i.14)
colnames(ipd.i.14)[2] <- 2014
ipd.i.15 <- mb.gather(ipd.i.15)
colnames(ipd.i.15)[2] <- 2015
ipd.i.16 <- mb.gather(ipd.i.16)
colnames(ipd.i.16)[2] <- 2016
#ipd.roc.i <- mb.gather(ipd.roc.i)
#colnames(ipd.roc.i)[2] <- "ROC incidence"

ipd.prev <- mb.gather(ipd.prev)
colnames(ipd.prev)[2] <- 2017
ipd.p.12 <- mb.gather(ipd.p.12)
colnames(ipd.p.12)[2] <- 2012
ipd.p.13 <- mb.gather(ipd.p.13)
colnames(ipd.p.13)[2] <- 2013
ipd.p.14 <- mb.gather(ipd.p.14)
colnames(ipd.p.14)[2] <- 2014
ipd.p.15 <- mb.gather(ipd.p.15)
colnames(ipd.p.15)[2] <- 2015
ipd.p.16 <- mb.gather(ipd.p.16)
colnames(ipd.p.16)[2] <- 2016
#ipd.roc.p <- mb.gather(ipd.roc.p)
#colnames(ipd.roc.p)[2] <- "ROC prevalance"

@@

ipd.i <- list( ipd.i.12, ipd.i.13,ipd.i.14,ipd.i.15,ipd.i.16,ipd.incidence) %>% reduce(left_join, by = "Location")

ipd.p <- list( ipd.p.12, ipd.p.13,ipd.p.14,ipd.p.15,ipd.p.16,ipd.incidence) %>% reduce(left_join, by = "Location")

@@

# Run function and change name
ad.incidence <- mb.gather(ad.incidence)
colnames(ad.incidence)[2] <- 2017

ad.i.12 <- mb.gather(ad.i.12)
colnames(ad.i.12)[2] <- 2012
ad.i.13 <- mb.gather(ad.i.13)
colnames(ad.i.13)[2] <- 2013
ad.i.14 <- mb.gather(ad.i.14)
colnames(ad.i.14)[2] <- 2014
ad.i.15 <- mb.gather(ad.i.15)
colnames(ad.i.15)[2] <- 2015
ad.i.16 <- mb.gather(ad.i.16)
colnames(ad.i.16)[2] <- 2016
#ad.roc.i <- mb.gather(ad.roc.i)
#colnames(ad.roc.i)[2] <- "ROC incidence"

ad.prev <- mb.gather(ad.prev)
colnames(ad.prev)[2] <- 2017
ad.p.12 <- mb.gather(ad.p.12)
colnames(ad.p.12)[2] <- 2012
ad.p.13 <- mb.gather(ad.p.13)
colnames(ad.p.13)[2] <- 2013
ad.p.14 <- mb.gather(ad.p.14)
colnames(ad.p.14)[2] <- 2014
ad.p.15 <- mb.gather(ad.p.15)
colnames(ad.p.15)[2] <- 2015
ad.p.16 <- mb.gather(ad.p.16)
colnames(ad.p.16)[2] <- 2016
#ad.roc.p <- mb.gather(ad.roc.p)
#colnames(ad.roc.p)[2] <- "ROC prevalance"

@@

ad.i <- list( ad.i.12, ad.i.13,ad.i.14,ad.i.15,ad.i.16,ad.incidence) %>% reduce(left_join, by = "Location")

ad.p <- list( ad.p.12, ad.p.13,ad.p.14,ad.p.15,ad.p.16,ad.incidence) %>% reduce(left_join, by = "Location")

library(reshape)
as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}

mnd.i.melt = melt(mnd.i, id = 'Location')
mnd.i.melt$variable <- as.numeric.factor(mnd.i.melt$variable)
ggplot(mnd.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="mnd Incidence") + 
  xlab("Year")

mnd.p.melt = melt(mnd.i, id = 'Location')
mnd.p.melt$variable <- as.numeric.factor(mnd.p.melt$variable)
ggplot(mnd.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="mnd Prevalance") + 
  xlab("Year")

ipd.i.melt = melt(ipd.i, id = 'Location')
ipd.i.melt$variable <- as.numeric.factor(ipd.i.melt$variable)
ggplot(ipd.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="ipd Incidence") + 
  xlab("Year")

ipd.p.melt = melt(ipd.i, id = 'Location')
ipd.p.melt$variable <- as.numeric.factor(ipd.p.melt$variable)
ggplot(ipd.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="ipd Prevalance") + 
  xlab("Year")

ad.i.melt = melt(ad.i, id = 'Location')
ad.i.melt$variable <- as.numeric.factor(ad.i.melt$variable)
ggplot(ad.i.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="AD Incidence") + 
  xlab("Year")

ad.p.melt = melt(ad.i, id = 'Location')
ad.p.melt$variable <- as.numeric.factor(ad.p.melt$variable)
ggplot(ad.p.melt, aes(x = variable, y = value, colour = Location)) + 
  geom_line() + 
  ylab(label="AD Prevalance") + 
  xlab("Year")
